data processing

### 2024-03-11 scRNAseq/processing.Rmd
fixed IDs

study <- read.csv(file.path(path,'sample_sheet','s_hegazy_IBD.txt'),
                 sep='\t') %>%
  dplyr::mutate(Sample.Name=gsub('p','P',Sample.Name))

assay <- read.csv(file.path(path,'sample_sheet','a_hegazy_IBD_totalseq_nucleotide_sequencing.txt'),
                 sep='\t') %>%
  dplyr::mutate(Sample.Name=gsub('p','P',Sample.Name),
                Library.Name=gsub('p','P',Library.Name))

for (lib in grep('CD4',samples,value=TRUE)) {
  sobj <- readRDS(file.path(path,'seurat',paste0(lib,'.rds')))
  vireo <- read.table(file.path(path,'vireo',paste0(lib,'_donor_ids.tsv')),
                      header=1,row.names=1,as.is=TRUE)
  colnames(vireo) <- paste0('vireo_',colnames(vireo))
  sobj <- AddMetaData(sobj, vireo)  
  sobj$vireo_donor_id[is.na(sobj$vireo_donor_id)] <- 'none'
  samples <- assay %>% 
    dplyr::filter(Library.Name==lib) %>% 
    dplyr::select(Parameter.Value.Multiplex.sample.tag.,Sample.Name) %>%
    dplyr::mutate(ht=Parameter.Value.Multiplex.sample.tag.) %>%
    dplyr::mutate(ht=ifelse(ht=='','Negative',gsub('_','-',ht))) 
  samples <- setNames(as.character(samples$Sample.Name), samples$ht)
  sobj$sample <- revalue(sobj$hash.ID, samples)
  print(table(sobj$sample,sobj$vireo_donor_id))
  sobjs <- SplitObject(sobj,split.by='sample')
  for (sample in samples) {
    pbmc[[sample]] <- sobjs[[sample]]
  }
}
```

>>>>

libraries <- read.csv("libraries.txt", sep='\t')

for (lib in grep('CD4',samples,value=TRUE)) {
  sobj <- readRDS(file.path(path,'seurat',paste0(lib,'.rds')))
  vireo <- read.table(file.path(path,'vireo',paste0(lib,'_donor_ids.tsv')),
                      header=1,row.names=1,as.is=TRUE)
  colnames(vireo) <- paste0('vireo_',colnames(vireo))
  sobj <- AddMetaData(sobj, vireo)  
  sobj$vireo_donor_id[is.na(sobj$vireo_donor_id)] <- 'none'
  samples <- libraries %>% 
    dplyr::filter(Library.Name==lib) %>% 
    dplyr::select(Parameter.Value.Multiplex.sample.tag.,Sample.Name) %>%
    dplyr::mutate(ht=Parameter.Value.Multiplex.sample.tag.) %>%
    dplyr::mutate(ht=ifelse(ht=='','Negative',gsub('_','-',ht))) 
  samples <- setNames(as.character(samples$Sample.Name), samples$ht)
  sobj$sample <- revalue(sobj$hash.ID, samples)
  print(table(sobj$sample,sobj$vireo_donor_id))
  sobjs <- SplitObject(sobj,split.by='sample')
  for (sample in samples) {
    pbmc[[sample]] <- sobjs[[sample]]
  }
}
```
